---
title: "PUT YOUR TITLE HERE"
author: "PUT YOUR NAME HERE"
output: html_notebook
---

**BELOW ARE INSTRUCTIONS FOR HOW TO COMPLETE THE ASSIGNMENT;
MAKE SURE THAT YOU DELETE ALL OF THE COMMENTS IN ALL CAPS
(AS WELL AS THIS COMMENT), BEFORE SUBMITTING**

THIS FIRST CHUNK SHOULD LOAD ALL OF THE PACKAGES (I THINK
YOU WILL NOT NEED TO CHANGE THIS)

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
library(readr)
library(ggplot2)
library(dplyr)
library(ggmap)
library(viridis)
library(forcats)
```

THE SECOND CHUNK SHOULD LOAD THE DATASET AND PRODUCE ANY
FILTERED DATASETS THAT YOU NEED IN THE REST OF THE REPORT

```{r}
tracts <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/acs_tract_data_2016.csv.gz")
```

NOW, YOUR REPORT SHOULD GO HERE. FEEL FREE TO SPLIT IT UP
WITH SECTIONS `##`, BUT THIS IS NOT REQUIRED. ADD CODE CHUNKS
TO PRODUCE GRAPHICS WHERE THEY BELONG IN THE OUTPUT

## References

IF YOU CITE ANY EXTERNAL SOURCES INCLUDE PARANTHETICAL
REFERENCES [SUCH AS: (Arnold, 2017)] IN THE TEXT AND
ADD CITATIONS HERE.


