---
title: "PUT YOUR TITLE HERE"
author: "PUT YOUR NAME HERE"
output: html_notebook
---

**BELOW ARE INSTRUCTIONS FOR HOW TO COMPLETE THE ASSIGNMENT;
MAKE SURE THAT YOU DETAIL ALL OF THE COMMENTS IN ALL CAPS
(AS WELL AS THIS COMMENT), BEFORE SUBMITTING**



# PUT YOUR TITLE HERE AGAIN by PUT YOUR NAME HERE AGAIN

## Overview

PUT AN INTRODUCTORY PARAGRAPH HERE GIVING IN 3-4 SENTENCES
THE BASIC IDEA OF YOUR DATA COLLECTION TASK AND HOW YOU WENT
ABOUT IT

## Schema

Here is a schema for the NAME HERE dataset:

(FOLLOW THE TEMPLATE HERE TO CREATE A SCHEMA)

- **VARIABLE1** (dbl): DESCRIPTION (UNITS)
- **VARIABLE2** (int): DESCRIPTION (UNITS)
- **VARIABLE2** (chr): DESCRIPTION
- ECT.

Which can be read in as follows:

YOU WILL HAVE TO UPLOAD THE DATASET FIRST TO GITHUB, THEN
FILL IN THE INFORMATION HERE

```{r}
DATANAME <- read_csv("https://raw.githubusercontent.com/urstats/YOUR_REPO_NAME/master/projects/YOUR_DATA_NAME.csv")
DATANAME
```

MAKE SURE TO PRINT OUT THE DATASET IN THE REPORT

## Univariate Analysis

### VARIABLE1

GIVE ABOUT 1-3 SENTENCES DESCRIBING THE DISTRIBUTION OR
VALUES FOUND IN VARIABLE 1, FOLLOWED BY A TABLE AND/OR
AND/OR MEAN, MEDIAN, SD, PERCENTILES, or DECILES (DON'T
BE EXCESIVE; JUST USE WHAT GETS THE POINT ACROSS BEST):

```{r}
qplot(DATANAME$VARIABLE1)
```

### VARIABLE2

GIVE ABOUT 1-3 SENTENCES DESCRIBING THE DISTRIBUTION OR
VALUES FOUND IN VARIABLE 2, FOLLOWED BY A TABLE OR PLOT
AS APPROPRIATE

```{r}
table(DATANAME$VARIABLE2)
```

### VARIABLE2

GIVE ABOUT 1-3 SENTENCES DESCRIBING THE DISTRIBUTION OR
VALUES FOUND IN VARIABLE 1, FOLLOWED BY A TABLE AND/OR
AND/OR MEAN, MEDIAN, SD, PERCENTILES, or DECILES (DON'T
BE EXCESIVE; JUST USE WHAT GETS THE POINT ACROSS BEST):

```{r}
deciles(DATANAME$VARIABLE1)
```

### VARIABLE1

GIVE ABOUT 1-3 SENTENCES DESCRIBING THE DISTRIBUTION OR
VALUES FOUND IN VARIABLE 1, FOLLOWED BY A TABLE OR PLOT
AS APPROPRIATE

```{r}
qplot(DATANAME$VARIABLE1)
```

## Exploratory Analysis

NOW, IN ABOUT 2-3 PARAGRAPHS ALONG WITH A COUPLE OF EMBEDDED
GRAPHS, EXPLORE A POTENTIALLY INTERESTING RELATIONSHIP IN THE
DATASET... DON'T OVERTHINK THIS; ANY RELATIONSHIP IS FINE AT
THIS POINT

```{r}
qplot(DATANAME$VARIABLE1, DATANAME$VARIABLE2)
```

YOU'LL PROBABLY WANT TO PUT THE PLOT IN THE MIDDLE OF THE
EXPORATORY ANALYSIS

## References

IF YOU GOT ANY DATA FROM A SOURCE THAT NEEDS TO BE CITED,
INCLUDE PARANTHETICAL REFERENCES [SUCH AS: (Arnold, 2017)]
IN THE TEXT AND CITATIONS HERE.

AND THEN YOUR DONE (AGAIN, PLEASE DELETE ALL OF THESE ANNOYING
COMMENTS THAT I PUT IN ALL CAPS)


