---
title: "PUT YOUR TITLE HERE"
author: "PUT YOUR NAME HERE"
output: html_notebook
---

**BELOW ARE INSTRUCTIONS FOR HOW TO COMPLETE THE ASSIGNMENT;
MAKE SURE THAT YOU DELETE ALL OF THE COMMENTS IN ALL CAPS
(AS WELL AS THIS COMMENT), BEFORE SUBMITTING**

IN THE FIRST CHUNK HERE, WHICH SHOULD BE SET TO NOT BE INCLUDED IN THE REPORT,
KEEP THIS knit LINE AND ALSO LOAD ALL OF THE LIBRARIES YOU NEED

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# REPEAT THE TITLE OF THE STUDY HERE

## Overview

PUT AN INTRODUCTORY PARAGRAPH HERE GIVING IN 4-5 SENTENCES
THE BASIC IDEA OF YOUR DATA COLLECTION TASK AND HOW YOU WENT
ABOUT IT. INCLUDE THE OVERARCHING RESEARCH QUESTION DESCRIBING
WHY YOU WERE INTERESTED IN THIS DATA

## Data dictionary

Here is a data dictionary for the NAME HERE dataset:

(FOLLOW THE TEMPLATE HERE TO CREATE A DATA DICTIONARY)

- **VARIABLE1**: DESCRIPTION
- **VARIABLE2**: DESCRIPTION
- **VARIABLE**: DESCRIPTION
- ECT.

Which can be read in as follows:

YOU SHOULD UPLOAD THE FINAL DATASET AS A CSV FILE TO GITHUB, THEN FILL IN
THE INFORMATION HERE (MAKE SURE TO CHANGE THE NAME OF THE DATANAME TO
SOMETHING REASONABLE AND FOLLOWING OUR NAMING CONVENTIONS):

```{r}
DATANAME <- read_csv("https://raw.githubusercontent.com/urstats/YOUR_REPO_NAME/master/YOUR_DATA_NAME.csv")
DATANAME
```

MAKE SURE TO PRINT OUT THE DATASET IN THE REPORT, AS THE CODE ABOVE WOULD DO

## Exploratory Analysis

NOW, IN ABOUT 2-3 PARAGRAPHS ALONG WITH A COUPLE OF EMBEDDED
GRAPHS, EXPLORE A POTENTIALLY INTERESTING RELATIONSHIP IN THE
DATASET. MAKE SURE THAT THE CODE TO CONSTRUCT THE PLOTS IS NOT INCLUDED IN THE
REPORT. ALSO MAKE SURE THAT THE PLOTS ARE WOVEN INTO THE ANALYSIS AND NOT JUST
DUMPED AT THE START OR END OF THE SECTION

```{r, echo=FALSE}
PLOT HERE
```

## Conclusion

WRITE JUST 2-4 SENTENCES DESCRIBING AT A HIGH LEVEL WHAT YOU LEARNED ABOUT
YOUR RESEARCH QUESTION FROM THE ANALYSIS. IF APPLICABLE, DESCRIBE WHAT OTHER
DATA OR VARIABLES YOU WOULD LIKE TO ADD TO LEARN MORE ABOUT THE QUESTION OF
INTEREST.

## References

IF YOU GOT ANY DATA FROM A SOURCE THAT NEEDS TO BE CITED,
INCLUDE PARANTHETICAL REFERENCES [SUCH AS: (Arnold, 2017)]
IN THE TEXT AND CITATIONS HERE.

AND THEN YOU ARE DONE (THOUGH AGAIN, PLEASE DELETE ALL OF THESE ANNOYING
COMMENTS THAT I PUT IN ALL CAPS)


