---
title: "Lab 17: Numeric Summaries"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)

library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(forcats)
library(smodels)
library(ggrepel)
theme_set(theme_minimal())
```

## Instructions

Below you will find several empty R code scripts and answer prompts. Your task
is to fill in the required code snippets and answer the corresponding
questions.

## Cereal Data

Today, we start by looking at a collection of breakfast cereals:

```{r}
cereal <- read_csv("https://statsmaths.github.io/stat_data/cereal.csv")
```

With variables:

- name: name of the specific cereal
- brand: name of the cereal's manufacturer
- sugar: amount of sugar per serving (g)
- score: healthiness score; 0-100; 100 is the best
- shelf: what shelf the cereal is typically stocked on in the store

Produce a histogram of the sugar variable.

```{r}

```

Now, compute the standard deviation of the variable `sugar`:

```{r}

```

What are the units of this measurement?


**Answer**:

Now, compute the deciles of the variable `score`:

```{r}

```

What is the value of the 30th percentile. Describe what this means in words:

**Answer**:

Produce a boxplot of score and brand.

```{r}

```

Which brand seems to have the healthiest cereals?

**Answer**:

Produce a boxplot of score and shelf.

```{r}

```

Produce a boxplot of sugar and shelf.

```{r}

```

If I want a healthy but reasonably sweet cereal which shelf would be the
best to look on?

**Answer**:

## Tea Reviews

Next, we will take another look at a dataset of tea reviews that I used in
a previous lecture:

```{r}
tea <- read_csv("https://statsmaths.github.io/stat_data/tea.csv")
```

With variables:
- name: the full name of the tea
- type: the type of tea. One of:
    - black
    - chai
    - decaf
    - flavors
    - green
    - herbal
    - masters
    - matcha
    - oolong
    - pu_erh
    - rooibos
    - white
- score: user rated score; from 0 to 100
- price: estimated price of one cup of tea
- num_reviews: total number of online reviews

Draw a scatterplot with num_reviews (x-axis) against score (y-axis) and add a
regression line (recall: `geom_smooth(method="lm")`).

```{r}

```

Does the score tend to increase, decrease, or remain the same as the number
of reviews increases?

**Answer**:

Calculate the ventiles of the variable price.

```{r}

```

What is the 80th percentile? Describe it in words, include the units of the
problem in your answer.

**Answer**:

Plot the number of reviews (x-axis) against the score variable. Color
the points according to price binned into 5 buckets.

```{r}

```

What tends to be true about the number of reviews for the most expensive
20% of teas?

**Answer**:

Create a dataset named `white` that consists of only white teas.

```{r}

```

Calculate the standard deviation of the price for white teas and the
standard deviation of the price for all of the teas.

```{r}

```

Is the variation of the white tea prices smaller, larger, or about the same
as the entire dataset?

**Answer**:

Summarize the dataset by the type of tea and save the results as a variable
named `tea_type`.

```{r}

```

Plot the average price (x-axis) against the average score (y-axis) of
each type  of tea. Make the size of the points proportional to the number
of teas in each category and label the points with geom_text_repel and the
tea type.

```{r}

```

Describe an interesting pattern or set of outliers that you found in the
previous plot. This does not need to take more than 1-2 sentences.

**Answer**:


