---
title: "Numeric Summaries"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class05-numeric-summaries/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(smodels)
library(kableExtra)
```

### Variable Types

These notes use a set of data describing the commuting patterns in
906 metropolitan areas within the United States.

```{r, message = FALSE}
commute <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/acs_commute.csv")
```
```{r, echo = FALSE}
commute <- commute[,c("name", "lat", "lon", "prop_housing", "median_income",
                      "avg_duration", "median_age", "same_house",
                      "same_county", "car_alone", "public_transit",
                      "time_0900_0959")]
commute
```

The variables available for analysis are described by the following
data dictionary and schema:

- **name** (chr): name of the metropolitan or micropolitan area
- **lat** (dbl): latitude of the centroid of the area
- **lon** (dbl): longitude of the centroid of the area
- **prop_housing** (dbl): average proportion of income spent on housing (0-100)
- **median_income** (dbl): median annual household income (dollars)
- **avg_duration** (dbl): average duration of commute (in minutes)
- **median_age** (dbl): median age of all people in the area
- **same_house** (dbl): proportion of households in the same house one year prior (0-100)
- **same_county** (dbl): proportion of households in the same county one year prior (0-100)
- **car_alone** (dbl): proportion of workers commuting by car alone (0-100)
- **public_transit** (dbl): proportion of workers commuting by public transit (0-100)
- **time_0900_0959** (dbl): proportion of workers commuting to work between 9am and 10am (0-100)

We will look more closely at this interesting dataset throughout
the week.

### Measures of Central Tendency

A common measurment of the *typical* value of a numeric variable
is the average or mean, mathematically described by:

$$ \text{mean}(x) = \frac{x_1 + x_2 + \cdots + x_n}{n} $$

As we have seen, the function `mean` in R computes this summary
for a numeric variable. Here is the average duration of commutes
in the US metropolitan areas (in minutes):

```{r}
mean(commute$avg_duration)
```

The average percentage, across areas, of commuters who drive alone
to work:

```{r}
mean(commute$car_alone)
```

The median is another measurment of the most typical values of a variable,
defined as the number for which half of the data is above and half of the
data is below the value (rules exist for taking the median of variables
with ties and even number of points, but the specifics are not important).

```{r}
median(commute$avg_duration)
```

Notice that this is not very different from the `mean` function. What is
an example of a variable that would differ greatly between the mean and
the median?

### Measures of Distribution

The median can also be described as the 50 percentile. Other percentiles
can be found with the `percentiles` function:

```{r}
percentiles(commute$public_transit)
```

Can you describe what the 25 percentile means, roughly speaking? Often
we only want the *deciles* of a variable, for which the `deciles` function
is used:

```{r}
deciles(commute$avg_duration)
```

How do these eleven numbers tell a bigger picture than the single mean or
median?

### Measures of Variation

In addition of measuring percentiles, often it is useful to give a single
number to describe how spread out a variable is. One common measurment is
the variance, the average distance of points from the mean:

$$ \text{var}(x) = \frac{(x_1 - mean(x))^2 + (x_2 - mean(x))^2 + \cdots + (x_n - mean(x))^2}{n - 1} $$

If we take the variance of the `avg_duration` variable:

```{r}
var(commute$median_income)
```

What are the units? Dollars-squared. That doesn't make much sense, so often
we take the square root of the variance instead to arrive at the standard
deviation:

$$ \text{sd}(x) = \sqrt{\text{var}(x)} $$

Which is computed with the `sd` function:

```{r}
sd(commute$median_income)
```

Higher standard deviations indicate that the variable is spread over a larger
range and lower deviations indicate that the variable is spread over a smaller
range.

### Standard Deviation Rules

The standard deviation can feel a bit abstract, but it is best to think
of it as a rough measurment of how far data tends to be away from the mean.
For example, take the mean of the median age across the metropolitan areas:

```{r}
mean(commute$median_age)
```

And the standard deviation of this variable.

```{r}
sd(commute$median_age)
```

As a general rule, we would expect 66% of the data to be within 1
standard deviation of the mean. That is, two-thirds of the metropolitan
areas should have median ages between 33.6 and 43.2 years.
Similarly, 95% of the data should be within two standard deviations of
the mean. That is, between 28.8 and 48 years.

```{r, message = FALSE}
qplot(median_age, data = commute)
```

Does the graphic confirm these rules of thumb? Note that the rules
generally apply only to data that is (very) roughly shaped like a bell
curve.
