---
title: "Class 15: Peer Review, Project B"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class13-forcats/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)

theme_set(theme_minimal())
```

### Objectives

Today, you will be peer-reviewing three other project B reports. As a first 
step, please add links to the first two projects on your website and make sure
you include the titles of the projects.

### Peer-review

Please comment separately on the three graphics, the text, and the overall
project. I suggest reading the entire project and then go back and answer the
questions. Try to focus on constructive feedback. Leave the review sheet with 
the person's computer (though please do not read others reviews in order to
not bias yourself ahead of time).



