---
title: "Variable Types"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class08-variable-types/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
```

### Variable Types

Variables in R have different *types* depending on the kind of
data that they store. The most common types that you will see
are the following three:

- integers (whole numbers)
- doubles (decimal numbers)
- characters

Mostly, you won't need to worry about the difference between
integers and doubles. R with treat them very similarly. However,
character vectors are handled quite distinctly from numeric
data. There are many other data types that you might encounter;
two other relatively common data types deal with time data:

- dates (day, month, and year)
- date-times (date plus hour, seconds, and possibly sub-second info)

Let's look at a new dataset to see examples of the kinds of data that
can be stored in a data frame:

```{r, message = FALSE}
birds <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/birds.csv")
```
```{r, echo = FALSE}
birds <- birds[birds$type %in% names(sort(table(birds$type), decreasing = TRUE))[1:15],]
head(birds, 10) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

Do any of the data types surprise you? Hopefully not!

### Schema / Data Dictionary

We have already discussed a data dictionary. A schema is simply
a data dictionary that also includes a description of the data
types. Here is a data dictionary of the birds data:

- **genus** (chr): taxonomic rank of the bird
- **species** (chr): scientific species name of the bird
- **name** (chr): common name of the bird
- **type** (chr): common name of the type of bird
- **egg_mass** (dbl): average mass of an egg when laid (grams)
- **male_mass** (dbl): average observed mass of an adult male (grams)
- **mating_system** (int): scores of mating system. Intensity of male-male competition increases from 1 to 5.
    - (1) polyandry
    - (2) monogamy (<5% polygyny)
    - (3) mostly monogamy, but occasional polygyny (5–15% polygyny)
    - (4) mostly polygyny (> 15% polygyny)
    - (5) lek or promiscuous
- **display** (int): mating display agility
    - (1) ground displays only, including displays on trees and bushes
    - (2) ground displays, but with occasional jumps/leaps into the air
    - (3) both ground and non-acrobatic flight displays
    - (4) mainly aerial displays, non-acrobatic
    - (5) mainly aerial displays, acrobatic
- **resource** (int): scores of territoriality and between-mate resource sharing
    - (0) males and females don't share resources and they feed away from their breeding territory
    - (1) males and females share resources on their territory only during the breeding season
    - (2) males and females share resources on their territory all year round.
- **clutch_size** (dbl): average number of eggs produced per clutch

Notice that the last two variables are integer codes. They are
stored as numbers but also correspond to a category. The schema
describes this in detail.

### Plot by Variable Type

One reason that we care about data types is that it changes
the types of plots that we can create. Here is a scatter plot
of two numeric variables:

```{r}
qplot(birds$male_mass, birds$egg_mass)
```

And a bar plot of a categorical one:

```{r, message = FALSE}
qplot(type, data = birds)
```

Other functions related to graphics and modelling also change
based on the type of a variable, so it is quite important to
make a note of these.

### Converting to Characters

We can use the `as.character` function to convert from a number
to a category. For example, here is a bar plot of the display
integer codes:

```{r, message = FALSE}
qplot(as.character(birds$display))
```

Does it make sense in this context to describe the display variable
as a categorical variable?

### Grouping Numeric Data

We can also use the `cut` function to break a numeric variable into
contiguous groups. We have to specify the number of groups in a second
argument to the function, like this:

```{r}
qplot(cut(birds$egg_mass, breaks = 4))
```

The function breaks the range of the numeric variable into equal chunks.
Unlike the `as.character` function, the `cut` function makes sense for
any numeric variable. Would `as.character` be useful on the variable
`egg_mass`?



