---
title: "Class 16: Presentations, Project B"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class16-presentations-project-b/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)

theme_set(theme_minimal())
```

For this class, we have presentations of students' work from the second 
project. 

**Section 01**:

- Margaret Kane: [Baltimore, Maryland](../assets/project-b/mkane.html)
- Byongho Lee: [Chilling in Colorado](../assets/project-b/blee.html)
- Andrea Celleri [Chicago](../assets/project-b/acelleri.html)
- Jacob Jacisin [Boston Metropolitan Area Trends](../assets/project-b/kjacisin.html)
- Ian Evans [Insights into the Tri-State Area](../assets/project-b/ievans.html)
- Sydney Gardner [Poverty in Delaware](../assets/project-b/sgardner.html)
- Nico Zingarelli [Cost Burdenedness in San Francisco](../assets/project-b/nzigarelli.html)
- Lilian Nguyen [The South](../assets/project-b/lnguyen.html)
- Troy Wu [Effects of Migration from the Northeast on Las Vegas](../assets/project-b/twu.html)
- Rosie Armstrong [Visualizing Communities in Fairfield County](../assets/project-b/rarmstrong.html)

**Section 02**:




