---
title: "Describing Data"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class07-describing-data/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
```

### Consistency

As you saw last week with our class data collection task, it is very important
to be consistent in the way that we represent data. If one student describes
a restaurant as 'Indian' and another describes it as 'indian', R will treat
these as completely different values. Likewise, if we input a variable as
'$14.50' R will treat this as a string rather than a number.

It is possible to convert a dataset with inconsistent data within R. This
process is called **data cleaning**; we often refer to data that is not
consistent as being **messy**. Learning how to clean data, however, is
relatively difficult. No two datasets are messy in the same way, and the
process involves using dozens of functions, often in fairly complex ways. It
is MUCH easier to make sure that data is clean before reading it into R.

We will try to be consistent in our data entry and coding practices in two
ways: (1) by establishing some basic coding guidelines and (2) by documenting
any additional decisions that we make. We will talk about both of these in
turn today.

### Data rules and dictionary

How should we go about structuring a dataset? Try to follow these guidelines:

- start by identifying the object of study; then, each row represents one
object of study (in the future, we may have datasets that have multiple
objects; we'll get to that later)
- then determine what the variables are; each column should be indivisible;
for example, cost of a meal should not include the dollar sign; if we are
working with multiple currencies, create a new column to contain the name of
the currency
- always have internal consistency (0.62 or 62 percent; missing values always
"NA"); strive for external consistency (ISO currency code: use "USD" instead
of "dollars" in a currency column)

Once we have decided how to structure a dataset, it is
important to document exactly what each
variable in a dataset is describing. A description of all the
variables in a dataset is called a **data dictionary**. Often
these seem self-explanatory, but it is still useful to briefly
describe all of the variables. Here is an example of a data
dictionary for the births dataset:

- **head_of_state**: who was the Head of State for the country
representing London
- **year**: calendar year of the dataset
- **boys**: number of male baptised in London in a given year
- **girls**: number of female baptised in London in a given year
- **total**: total number of children baptised in London in a given year
- **boy_to_girl_ratio**: ratio of male births to female births
in London in a given year

Notice that you could probably guess the basic meaning of many of these,
but may not have been aware of some of the specifics.

### Style Guide

In order to make your code easily readable by others, it is
important to follow certain rules in how you create code. In
programming a collection of such rules is known as a style
guide.

One of the most important rules that we will follow is to
create consistent variable names:

- use all lower case letters in variable names
- never use spaces; use an underscore `_` instead (e.g., `head_of_state`)
- do not use numbers unless they have an extrinsic meaning (so `year_1990`
is okay, but `births2` is not)

These variable rules apply to raw R objects as well as the column names in
your dataset.

Other rules that we will follow (some of these may not make sense
yet):

- keep code lines no longer than 79 characters, other than URLs
- group code into blocks separated by single new line
- use only <- for assignment
- one space around the arrow <- and parameter names
- indent continuation lines to the proper point

For example, only the first line here follows the guidelines:

```{r, eval=FALSE}
photo <- mean(data$variable)
photo<- mean(data$variable)
photo <-mean(data$variable)
```

These details may seem unimportant, but trust me that sticking to
them will greatly simplify your ability to read and debug R code.
I will expect you to follow these rules in all of the work you
do in this course.

### Project A

We now have covered all of the skills needed to get started with the first
project. You can see a link to the project's describe and rubric on the course
website.

In order to work on the project, you'll need to use a a format called
**Rmarkdown**. It is similar, but distinct, from the `.R` files we
have been using up to this point. We can open a template, from which you can
work from, here:

[Project A Template](https://raw.githubusercontent.com/statsmaths/stat209/master/projects/project-a.Rmd)

By opening an Rmarkdown file in RStudio, we can turn the file
into a number of other formats. If I hit the *preview* button above, it will
display what the HTML version of the document looks like. I'll usually
export this HTML version and put it on the class website
as it is slightly cleaner than the raw format.

The most powerful feature of **Rmarkdown** is that we can
intermix code into the document and actually run it in real
time. To do this, we enclose code blocks with three back ticks,
and preface the first one with r in squiggly brackets. Every
code block will get run in sequence if when we hit the Preview
or Knit buttons, but we can also run just this block by hitting
the play button to the right of the block.



