---
title: "Data Basics"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class02-data-basics/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
```

### Loading Data

To load a dataset stored as a comma seperated file, we will use the
function `read_csv`. We will discuss the csv format more in the
next class. For now, here is the code for loading the Arbuthnot
dataset into R and storing as a variable called `births`:

```{r, message = FALSE}
births <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/arbuthnot.csv")
```

Interactively in RStudio, you can see the data by clicking on the
table in the upper right-hand corner. Here, we will look at the first
few rows of data as a table:

```{r, echo=FALSE}
head(births) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

This is a relatively well-known dataset collected in the 17th century
to study the secondary sex ratio (ratio of of males to females at birth)
using baptism records.

### Data Frames

In this course we will store data in a tabular format.
These tables will have **observations** stored in rows and
**variables** stored in columns. So, each row represents a
particular object in our dataset and each column represents
some feature of the objects.

As an example, let's read in the Arbuthnot dataset again:

```{r, message = FALSE}
births <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/arbuthnot.csv")
```
```{r, echo = FALSE}
head(births, 10) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The observations here correspond to a particular year. Each
variable describes something *about* that year. What exactly
constitutes a row of the data is called a **unit of analysis**.
Keeping in mind what the unit of analysis is will be very
important as we think about how data is being used.

The type of R object that stores such a dataset is called a
**data frame**.

### Accessing data variables

Often it will be useful to access a single variable within
a data frame by name. To do so, we use the name of the data
frame, followed by a dollar sign, followed by the name of
the variable. For example, here are all of the female births
in the dataset:

```{r}
births$girls
```

The function `mean` computes the average of a numeric variable.
Here we use this function to compute the average number of female
births in the dataset:

```{r}
mean(births$girls)
```

Similarly, you could compute the average number of male births
or total births.

### Comma seperated values

Data frames store tabular data for us within R. We also need a
way to store tabular data as a file. One option would be to store
data as Google sheets or Excel file. While these programs are
great for data input, it is not a good idea to store raw data in
these formats. Instead, we want a minimal **plain text** format.
That is, the file should be readable by any basic text editor.

The plan text data format that we will use is called a
**comma-separated values** or CSV file. In this format, each
column of the data is (as the name suggests) seperated by a
comma. Every observation is stored on its own row. The first
row gives the names of the columns. Here are what the first few
rows of the Arbuthnot dataset look like stored as a CSV file:

```
head_of_state,year,boys,girls,total,boy_to_girl_ratio
Charles I,1629,5218,4683,9901,1.114
Charles I,1630,4858,4457,9315,1.09
Charles I,1631,4422,4102,8524,1.078
Charles I,1632,4994,4590,9584,1.088
Charles I,1633,5158,4839,9997,1.066
Charles I,1634,5035,4820,9855,1.045
```

A CSV file can be created and read by R, Excel, GoogeSheets,
OpenOffice, and most other data processing and statistical tools.
It is one of the most common formats that you will see data stored
as online. By convention, a CSV file has the extension ".csv".

### Style Guide

In order to make your code easily readable by others, it is
important to follow certain rules in how you create code. In
programming a collection of such rules is known as a style
guide.

One of the most important rules that we will follow is to
create consistent variable names:

- use all lower case letters in variable names
- never use spaces; use an underscore `_` instead (e.g., `head_of_state`)
- do not use numbers unless they have an extrinsic meaning (so `year_1990`
is okay, but `births2` is not)

These variable rules apply to raw R objects as well as the
column names in your dataset.

Other rules that we will follow (some of these may not make sense
yet):

- keep code lines no longer than 79 characters, other than URLs
- group code into blocks separated by single new line
- use only <- for assignment
- one space around the arrow <- and parameter names
- indent continuation lines to the proper point

For example, only the first line here follows the guidelines:

```
photo <- mean(data$variable)
photo<- mean(data$variable)
photo <-mean(data$variable)
```

These details may seem unimportant, but trust me that sticking to
them will greatly simplify your ability to read and debug R code.
I will expect you to follow these rules in all of the work you
do in this course.

