---
title: "Data Basics"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class03-describing-data/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
```

### Data Dictionary

It is important to understand and document exactly what each
variable in a dataset is describing. A description of all the
variables in a dataset is called a **data dictionary**. Often
these seem self-explanatory, but it is still useful to briefly
describe all of the variables. Here is an example of a data
dictionary for the Arburthnot dataset:

- **head_of_state**: who was the Head of State for the country
representing London
- **year**: calendar year of the dataset
- **boys**: number of male baptised in London in a given year
- **girls**: number of female baptised in London in a given year
- **total**: total number of children baptised in London in a given year
- **boy_to_girl_ratio**: ratio of male births to female births
in London in a given year

Notice that you probably guess the basic meaning of many of these,
but may not have been aware of some of the specifics.

