---
title: "Variable Types"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class04-variable-types/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
```

### Variable Types


- integers
- doubles
- characters
- dates
- date-times


```{r, message = FALSE}
birds <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/birds.csv")
```
```{r, echo = FALSE}
birds <- birds[birds$type %in% names(sort(table(birds$type), decreasing = TRUE))[1:15],]
head(birds, 10) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Schema / Data Dictionary

- **genus** (chr): taxonomic rank of the bird
- **species** (chr): scientific species name of the bird
- **name** (chr): common name of the bird
- **type** (chr): common name of the type of bird
- **egg_mass** (dbl): average mass of an egg when laid (grams)
- **male_mass** (dbl): average observed mass of an adult male (grams)
- **mating_system** (int): scores of mating system. Intensity of male-male competition increases from 1 to 5.
    - (1) polyandry
    - (2) monogamy (<5% polygyny)
    - (3) mostly monogamy, but occasional polygyny (5–15% polygyny)
    - (4) mostly polygyny (> 15% polygyny)
    - (5) lek or promiscuous
- **display** (int): mating display agility
    - (1) ground displays only, including displays on trees and bushes
    - (2) ground displays, but with occasional jumps/leaps into the air
    - (3) both ground and non-acrobatic flight displays
    - (4) mainly aerial displays, non-acrobatic
    - (5) mainly aerial displays, acrobatic
- **resource** (int): scores of territoriality and between-mate resource sharing
    - (0) males and females don't share resources and they feed away from their breeding territory
    - (1) males and females share resources on their territory only during the breeding season
    - (2) males and females share resources on their territory all year round.
- **clutch_size** (dbl): average number of eggs produced per clutch


### Plot by Variable Type

```{r}
qplot(male_mass, egg_mass, data = birds)
```

```{r, message = FALSE}
qplot(type, data = birds)
```

### Converting to Characters


```{r, message = FALSE}
qplot(as.character(birds$display))
```

### Grouping Numeric Data

```{r}
qplot(cut(birds$egg_mass, breaks = 4))
```

