---
title: "Numeric Summaries"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class04-numeric-summaries/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
```

### Variable Types

```{r, message = FALSE}
commute <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/acs_commute.csv")
```
```{r, echo = FALSE}
commute <- commute[,c("name", "lat", "lon", "prop_housing", "median_income",
                      "avg_duration", "median_age", "same_house",
                      "same_county", "car_alone", "public_transit",
                      "time_0900_0959")]
commute
```

### Data Dictionary

- **name** (chr): name of the metropolitan or micropolitan area
- **lat** (dbl): latitude of the centroid of the area
- **lon** (dbl): longitude of the centroid of the area
- **prop_housing** (dbl): average proportion of income spent on housing (0-100)
- **median_income** (dbl): median annual household income (dollars)
- **avg_duration** (dbl): average duration of commute (in minutes)
- **median_age** (dbl): median age of all people in the area
- **same_house** (dbl): proportion of households in the same house one year prior (0-100)
- **same_county** (dbl): proportion of households in the same county one year prior (0-100)
- **car_alone** (dbl): proportion of workers commuting by car alone (0-100)
- **public_transit** (dbl): proportion of workers commuting by public transit (0-100)
- **time_0900_0959** (dbl): proportion of workers commuting to work between 9am and 10am (0-100)

### Measures of Central Tendency

$$ \text{mean}(x) = \frac{x_1 + x_2 + \cdots + x_n}{n} $$

```{r}
mean(commute$avg_duration)
```

```{r}
mean(commute$car_alone)
```

```{r}
median(commute$avg_duration)
```


### Measures of Distribution

```{r}
deciles(commute$avg_duration)
```

```{r}
percentiles(commute$public_transit)
```

### Measures of Variation

$$ \text{var}(x) = \frac{(x_1 - mean(x))^2 + (x_2 - mean(x))^2 + \cdots + (x_n - mean(x))^2}{n - 1} $$



$$ \text{sd}(x) = \sqrt{\text{var}(x)}


```{r}
sd(commute$median_income)
```

### Standard Deviation Rule (66-95-99.6)

```{r}
mean(commute$median_age)
```

```{r}
sd(commute$median_age)
```

Expect 66% of the data from 33.6 to 43.2 years and 95%
between 28.8 and 48 years.

```{r}
qplot(median_age, data = commute)
```
