---
title: "Analysis: Proportiong of Income Spent on Housing"
author: "Taylor Arnold"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(fig.path = "../assets/class06-analysis-prop-housing/")
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)
```

```{r, message = FALSE, include = FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(smodels)
library(kableExtra)
```

### ACS Commuting to Work Dataset

Today, we will again look at the data describing the commuting
patterns in 906 metropolitan areas within the United States.

```{r, message = FALSE}
commute <- read_csv("https://raw.githubusercontent.com/statsmaths/stat_data/gh-pages/acs_commute.csv")
```

Here is a description of just some of the variables available for
analysis:

- **name** (chr): name of the metropolitan or micropolitan area
- **lat** (dbl): latitude of the centroid of the area
- **lon** (dbl): longitude of the centroid of the area
- **prop_housing** (dbl): average proportion of income spent on housing (0-100)
- **median_income** (dbl): median annual household income (dollars)
- **avg_duration** (dbl): average duration of commute (in minutes)
- **median_age** (dbl): median age of all people in the area
- **same_house** (dbl): proportion of households in the same house one year prior (0-100)
- **same_county** (dbl): proportion of households in the same county one year prior (0-100)
- **car_alone** (dbl): proportion of workers commuting by car alone (0-100)
- **public_transit** (dbl): proportion of workers commuting by public transit (0-100)
- **time_0900_0959** (dbl): proportion of workers commuting to work between 9am and 10am (0-100)

Our variable of interest is to understand what factors drive people to
spend a large amount of their income on housing.

I would suggest addressing this question by drawing two-dimensional scatter
plots such as this:

```{r}
qplot(commute$lon, commute$lat)
```

But, use `prop_housing` as the y-variable.

## Project 1

### Markdown

This document, as well as all of the course's notes, is written
in a format called **Rmarkdown**. At the moment we are looking at the
compiled code; it is similar, but distinct, from the `.R` files we
have been using up to this point for the labs.

Plain markdown is just a very simple format for marking up
texts. Unlike writing text in a word editor, there is nothing
hidden in a markdown file. If you want something to be in
italics, surround it in single stars like *this*. For bold,
use **two**. Links use the following format:
[site name](http://www.wheretogo.com). If you want to make
something look like code in the output, you can enclose
text in back ticks: `print("Hello!")`.

By openning an Rmarkdown file in RStudio, we can turn the file
into a number of other formats. If I
hit the *preview* button above, it will display what the
HTML version of the document looks like. I'll usually
export this HTML version and put it on the class website
as it is slightly cleaner than the raw format.

The most powerful feature of **Rmarkdown** is that we can
intermix code into the document and actually run it in real
time. To do this, we enclose code blocks with three back ticks,
and preface the first one with r in squiggly brackets. Every
code block will get run in sequence if when we hit the Preview
or Knit buttons, but we can also run just this block by hitting
the play button to the right of the block. Here, let's add
1 and 1 together:

```{r}
1 + 1
```

Your projects will be submitted in RMarkdown. I will give you
a template with which to work from.

## GitHub Classroom

Let's now go through and show how to put these together to produce and submit
your daily labs. I will do this interactively in class, but here are
the steps in case you are returning to these notes at a later
time:

1. I will send a link to your e-mail that you should follow
and accept. Assuming you have a valid GitHub account, this
will set up a repository where all of your projects for this semester
should be posted.
2. Download the project starter code and open it in RStudio.
3. When you are finished, select the `Knit to HTML` button. This
should create an html file in the same location that you saved
the Rmd file. You should also have a file `class01_submit.csv`
in the same location.
4. Return to GitHub and drag and drop the three files into your
repository. Commit these to the repository with the **Commit changes**
button and then you are done! If dragging and dropping does not work
(only officially support on Chrome I believe), select **Upload files**
and do so manually.

Remember that I will not accept late submissions of the projects.
It is always better to hand *something* in on time.




